No meaningful effects of COVID-19 related social media use on well-being

### 2021-12-01 manuscript.Rmd
- updated website
- changed fig caption

```{r res-activity, fig.cap="The effects of various types of social media use on three indicators of well-being. The black estimates show the effects controlled for a large number of covariates (see text; preregistered); the grey estimates are without control variables (exploratory). The SESOI was \\textit{b} = |0.30| for life satisfaction and \\textit{b} = |0.15| for affect. Hence, all of the reported effects are considered not meaningful.", out.width = "\\textwidth", cache=F}
knitr::include_graphics("figures/fig_results_activity.pdf")
```

@@

```{r res-channels, fig.cap="The effects of using various social media applications on three indicators of well-being. The black estimates show the effects controlled for a large number of covariates (see text); the grey estimates are without control variables. The SESOI was \\textit{b} = |0.30| for life satisfaction and \\textit{b} = |0.15| for affect. Hence, all of the reported effects are considered not meaningful.", out.width = "\\textwidth", cache=F}
knitr::include_graphics("figures/fig_results_channel.pdf")
```

@@

```{r tab-aff-neg}
# apa_print(model_aff_neg_lmer)
# tab <- broom.mixed::tidy(model_aff_neg_lmer, conf.int = T) %>% 
#  select(term, estimate, conf.low, conf.high, p.value)
#  kable()
```

>>>>

```{r res-activity, fig.cap="The effects of various types of social media use on three indicators of well-being. The black estimates show the effects controlled for a large number of covariates (see text; preregistered); the grey estimates are without control variables (exploratory). The SESOI was b = |0.30| for life satisfaction and b = |0.15| for affect. Hence, all of the reported effects are considered not meaningful.", out.width = "\\textwidth", cache=F}
knitr::include_graphics("figures/fig_results_activity.pdf")
```

@@

```{r res-channels, fig.cap="The effects of using various social media applications on three indicators of well-being. The black estimates show the effects controlled for a large number of covariates (see text); the grey estimates are without control variables. The SESOI was b = |0.30| for life satisfaction and b = |0.15| for affect. Hence, all of the reported effects are considered not meaningful.", out.width = "\\textwidth", cache=F}
knitr::include_graphics("figures/fig_results_channel.pdf")
```

@@
